%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Roel-Junior Alejo Viernes}
\tagline{Computer Science BSc (Hons) Graduate}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \homepage{www.rjviernes.tech}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  \location{London, United Kingdom}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
   \github{github.com/rjviernes620} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
 \linkedin{linkedin.com/in/rjviernes620}
}
%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[page1sidebar]{Personal Statement}
Creative technologist and Computer Science graduate specialising in social-first storytelling, 
UGC short-form video and community engagement. 
I blend hands-on experience as a Faculty Social Media Assistant with a strong grounding in HCI 
to create content that is both highly engaging and insight-led. \\
From leading Clearing campaign video strategies to producing testimonials, facility spotlights and 
event coverage, I’m used to owning end-to-end workflows across planning, filming,
editing and publishing at pace. I’m now looking to bring my background in video production,
analytics-aware content planning and stakeholder collaboration into a Social 
Media Content Creator or Social Media Executive role, helping organisations grow their
online presence and tell stories that genuinely resonate with their audiences.
\\



\cvsection{Projects}
\smallskip

\smallskip
\textbf{HandTyper - Real-Time Gesture Recognition System} \\
\begin{itemize}
  \item Developed a real-time gesture recognition system using Python and OpenCV, enabling users to 
  control their computer through hand movements.
  \item The system utilized machine learning 
  algorithms to accurately interpret various hand gestures and British Sign Language (BSL), providing an 
  innovative solution 
  for accessibility and human-computer interaction.
\end{itemize}
\textbf{University Open Day Guides w/ NFC Tags} \\
\begin{itemize}
  \item To assist prospective students during the University Open Days whilst upholding the university's commitment to 
sustainability. I introduced a new interaction framework where staff members would have NFC tags linking towards
a digital guide for the University and the relevant event.
  \item This reduced the need for printed materials and 
allowed for easy access to information via smartphones whilst also providing a modern and interactive experience for visitors.
\end{itemize}
\textbf{University Events (Open Day + Outreach)} \\
\begin{itemize}
  \item I have also participated and assisted in the organisation, running and the marketing of various University and Faculty events including
Open Days and Outreach programs. During these events, I took on roles such as guiding
prospective students, providing information about courses and campus life,
and assisting with event logistics. 

  \item My involvement in these events has helped me develop strong communication
and interpersonal skills, as well as a deeper understanding of the university's offerings and student needs.
\end{itemize}




\newpage
\cvsection[page2sidebar]{Experience}

\cvevent{Faculty Social Media Assistant}{University of Greenwich}{June 2023 - Oct 2025}{Greenwich, London}
\begin{itemize}
\item Multidisciplinary Production: Managed the full lifecycle of technical video content for the Faculty of Engineering \& Science, bridging the gap between deep-tech research and user-facing digital storytelling.
\item Stakeholder Management: Partnered with Professors and Researchers to storyboard and render accessible content for major university campaigns.
\item Brand Growth: Owned social media channel management for the faculty, increasing publication frequency through streamlined content workflows.
\item \textbf{Key Achievement: 2024/25 Clearing Campaigns:}
\item Spearheaded the short-form video strategy, producing testimonials and facility showcases that drove audience engagement across faculty platforms.
\item Collaborated with central marketing to ensure 100\% brand consistency while translating complex engineering concepts for prospective students.
\end{itemize}
\divider

\cvevent{Student Ambassador}{University of Greenwich}{Oct 2022 -- Oct 2025}{Greenwich, London}
\begin{itemize}
\item This role had allowed me to work for multiple different departments within the University including UK Student Recruitment, Outreach as well as roles within my own faculty. I had to constantly adapt my workflow and stance to appease the different stakeholders that I worked with as well as ensuring the  I've furtherly received the University of Greenwich Instrumental Ambassador Award in 2024 for the contributions I've made in my role to the Scheme as a whole.

\end{itemize}

\divider

\cvevent{Teacher Assistant}{Brompton Academy}{Jan 2022 - Jul 2022}{Gillingham, Kent}
\begin{itemize}
\item As a Teacher Assistant for Brompton Academy, I was responsible for supporting Year 10 students with their learning in Business Studies. I assisted in lesson preparation, provided one-on-one support to students, and helped manage classroom activities to create a positive learning environment.
\end{itemize}


%\cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
