%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Roel-Junior Alejo Viernes}
\tagline{Computer Science BSc (Hons) Graduate}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \homepage{www.rjviernes.tech}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  \location{London, United Kingdom}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
   \github{github.com/rjviernes620} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
 \linkedin{linkedin.com/in/rjviernes620}
}
%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[page1sidebar]{Personal Statement}
A highly motivated Computer Science graduate with proven expertise in social media content creation, technical project development, and leadership within academic and ambassadorial roles. Skilled in conceptualising and producing for multimedia marketing campaigns, with hands-on experience in video production, editing, and campaign management for the University of Greenwich. Adaptable and effective in multidisciplinary environments, with a track record of engaging diverse stakeholders, leading student societies, and excelling in both independent and team-based projects. Recognised for innovative problem-solving, a passion for technology integration and automations, and a commitment to advancing digital engagement and technical excellence in every role undertaken.\\

\cvsection{Experience}

\cvevent{Faculty Social Media Assistant}{University of Greenwich}{June 2023 - Oct 2025}{Greenwich, London}
\begin{itemize}
\item  I create different pieces of content (specializing within videos) for the Social Media Channels for the Faculty of Engineering \& Science at the University and sometimes for the main University pages too. I facilitate the production of content from conceptualizing to editing and then publication. I've additionally participated within the content creation for various marketing campaigns in the University (Inc. Clearing, Open Days etc.) as well as starred as the main role within the University's Profile video for the Computer Science suite of degrees on YouTube. 
\end{itemize}

\divider

\cvevent{Student Ambassador}{University of Greenwich}{Oct 2022 -- Nov 2025}{Greenwich, London}
\begin{itemize}
\item This role had allowed me to work for multiple different departments within the University including UK Student Recruitment, Outreach as well as roles within my own faculty. I had to constantly adapt my workflow and stance to appease the different stakeholders that I worked with as well as ensuring the  I've furtherly received the University of Greenwich Instrumental Ambassador Award in 2024 for the contributions I've made in my role to the Scheme as a whole. 

\end{itemize}

\divider

\cvevent{Teaching Assistant}{Brompton Academy}{Jan 2022 -- Jul 2022}{Gillingham, Kent}
\begin{itemize}
\item This role involved me becoming a Teacher Assistant for a Year 10 Business Studies Class within my Secondary School. From assisting the students with understanding the material to help delivering lessons to assisting the Teacher with certain aspects of delivering their lesson as well as preparing and designing resources too. 


\end{itemize}
%\divider

\cvsection{Additional Roles}
\begin{itemize}
  \item  Programme Rep - Year 2 Computer Science (2023)
  \item comptech.gre (Computer and Tech Society) - President (Mar 2024 - May 2025)
  \item Senior UK Student Recruitment Ambassador (May 2024 - Present)
\end{itemize}

\cvsection{Projects}
\smallskip
\begin{itemize}
\item comptech.gre/hunt - An NFC based In-Person treasure hunt
\smallskip
\item Final Year Project: HandTyper - Hand Gesture based PC Interaction
\smallskip
\item University Open Day Guides w/ NFC Tags
\end{itemize}

%\cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\clearpage

% \cvsection[page2sidebar]{Publications}

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
