%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Roel-Junior Alejo Viernes}
\tagline{Computer Science BSc (Hons) Graduate}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \homepage{www.rjviernes.tech}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  \location{London, United Kingdom}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
   \github{github.com/rjviernes620} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
 \linkedin{linkedin.com/in/rjviernes620}
}
%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[page1sidebar]{Personal Statement}
A highly motivated Computer Science graduate with proven
expertise in video editing, technical project development
and management, and leadership/Team Leading within
academic and ambassadorial roles. I am Skilled in conceptualising
and producing content for marketing campaigns, I
have hands-on experience in handling sensitive data, editing,
and content management. I have led teams during
high-pressure Clearing operations for the University of
Greenwich and contributed to the training and mentoring
of new ambassadors joining the team. Adaptable and effective
in multidisciplinary environments, I have a track
record of engaging with diverse stakeholders, leading
student societies, and excelling in both independent and
team-based projects. Recognised for innovative problem
solving, a passion for technology integration and automations,
and a commitment to advancing digital engagement
and technical excellence, I bring a proactive, solutionsfocused
approach to every role I undertake.
\\



\cvsection{Projects}
\smallskip
\textbf{Final Year Project: HandTyper - Hand Gesture based PC Interaction} \\
\begin{itemize}
  \item Develop a real-time hand gesture recognition system as an alternative to traditional mouse and keyboard interaction.
  \item Use libraries such as Mediapipe, OpenCV, and TensorFlow to build a computer vision model that translates BSL signs into keyboard input and hand landmarks into mouse control.
  \item Implement landmark detection to track hand points and interpret gestures for corresponding computer input actions.
\end{itemize}
\smallskip
\textbf{University Open Day Guides w/ NFC Tags} \\
\begin{itemize}
  \item To assist prospective students during the University Open Days whilst upholding the university's
   commitment to sustainability. I introduced a new interaction framework where staff members would 
   have NFC tags linking towards a digital guide for the University and the relevant event. 
  \item This reduced the need for printed materials and allowed for easy access to information via 
   smartphones.
\end{itemize}
\textbf{Coursework Project: TAS Speedruns and the use of AI in Games} \\
\begin{itemize}
  \item This project invovled me and my coursework group researching into different ML algorithms which are commonly used within the controlling of CPU players in video games and creating our own implementations of ML algorithms to onto the game "Super Mario Bros" to create a CPU player which would be able to complete levels in the fastest time possible.
  \item My own implementation included the use of the MCTS (Monte Carlo Tree Search) algorithm and 
  pathfinding to create an AI agent which would be able to play through levels of Super Mario Bros.
\end{itemize}



\newpage
\cvsection[page2sidebar]{Experience}

\cvevent{Faculty Social Media Assistant}{University of Greenwich}{June 2023 - Oct 2025}{Greenwich, London}
\begin{itemize}
\item  Conceptualised and produced technical video content for the Faculty of Engineering \& Science, managing the full production lifecycle from storyboarding to final render.
\item Collaborated with technical stakeholders (Professors, Researchers) to translate complex engineering concepts into accessible digital content, demonstrating the ability to bridge the gap between deep tech and user experience.
\item Maintained brand consistency across multiple platforms, ensuring high-fidelity output for major university campaigns (Clearing, Open Days).
\item I've additionally participated within the content creation for various marketing campaigns in the University (Inc. Clearing, Open Days etc.) as well as starred in the University's Profile video for the Computer Science suite of degrees on YouTube.\end{itemize}

\divider

\cvevent{Senior UK Student Recruitment Ambassador}{University of Greenwich}{Oct 2022 -- Oct 2025}{Greenwich, London}
\begin{itemize}
\item This role had allowed me to work for multiple different departments within the University including UK Student Recruitment, Outreach as well as roles within my own faculty. I had to constantly adapt my workflow and stance to appease the different stakeholders that I worked with as well as ensuring the  I've furtherly received the University of Greenwich Instrumental Ambassador Award in 2024 for the contributions I've made in my role to the Scheme as a whole.

\end{itemize}

\divider

\cvevent{Teacher Assistant}{Brompton Academy}{Jan 2022 - Jul 2022}{Gillingham, Kent}
\begin{itemize}
\item As a Teacher Assistant for Brompton Academy, I was responsible for supporting Year 10 students with their learning in Business Studies. I assisted in lesson preparation, provided one-on-one support to students, and helped manage classroom activities to create a positive learning environment.
\end{itemize}


%\cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
