%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{0pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-8pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Roel-Junior Alejo Viernes} \\ \vspace{5pt}
    \small \faPhone* \texttt{+447719794481} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{roel@rjviernes.tech} \hspace{1pt} $|$ 
    \hspace{1pt} \faGlobe \hspace{2pt} \texttt{rjviernes.tech} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt}\texttt{rjviernes620} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{rjviernes}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior UK Student Recruitment Ambassador}{Jan 2023 -- Oct 2025}
      {University of Greenwich}{Greenwich, London}
      \resumeItemListStart
        \resumeItem{Led and coordinated a team of 10+ student ambassadors during high-pressure Clearing operations and campus events, ensuring a customer-centric and supportive environment for prospective students and families.}
        \resumeItem{Resolved complex student inquiries across CRM databases, LiveChat, phone support, and in-person tours, demonstrating excellent communication and problem-solving skills under pressure.}
      \resumeItemListEnd

    \resumeSubheading
      {Social Media \& Content Operations}{June 2023 -- Oct 2025}
      {University of Greenwich}{Greenwich, London}
      \resumeItemListStart
        \resumeItem{Coordinated digital content operations and multi-channel publishing calendars for the Faculty of Engineering \& Science, managing campaigns to promote academic events and student engagement.}
        \resumeItem{Partnered with researchers and academics to translate complex university offerings into accessible communication materials, serving as a key brand representative and on-camera advocate.}
      \resumeItemListEnd

    \resumeSubheading
      {Teacher Assistant}{Jan 2022 -- Jul 2022}
      {Brompton Academy}{Gillingham, Kent}
      \resumeItemListStart
        \resumeItem{Supported the delivery of lesson plans for Year 10 Business Studies classes, explaining business concepts to students and providing support to the lead teacher.}
        \resumeItem{Facilitated interactive group activities and discussions, boosting student participation and class engagement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Greenwich}{Sep. 2022 -- Jul. 2025}
      {Computer Science BSc (Hons)}{Greenwich, London}
       \resumeItemListStart
        \resumeItem {\textbf{Relevant Focus}: Project Management, Communication Systems, Human-Computer Interaction (HCI), Data Analysis}
        \resumeItem {\textbf{Dissertation}: HandTyper -- An interactive computer vision based system applying User Experience (UX) and Human-Computer Interaction (HCI) design principles.}
        \resumeItem {\textbf{Extra-Curricular}: President of the Computer Science Society (leading student events, budgeting, and operations), Student Representative, Student Ambassador}
        \resumeItem {\textbf{Achievements}: University of Greenwich Instrumental Ambassador Award, Faculty of Engineering \& Science Making a Difference Award}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS \& CONTRIBUTIONS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Clearing Campaigns} {2024 | 2025}
          \resumeItemListStart
            \resumeItem{Coordinated content creation and digital brand strategy for major student recruitment campaigns, serving as a key ambassador to connect with prospective students.}
            \resumeItem{Starred in promotional campaigns to represent the university's programs, facilitating outreach and engagement across multiple communication channels.}
          \resumeItemListEnd
      \resumeProjectHeading
          {NFC-Based Event Guides} {Python | HTML/CSS}
          \resumeItemListStart
            \resumeItem{Designed and launched interactive digital event guides for university guests, replacing print materials and improving navigation and accessibility at major events.}
            \resumeItem{Gathered and analyzed visitor engagement data to optimize guide design and improve the overall guest experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Customer Service}   {: Team Leadership, Public Speaking, Event Planning, Customer Support (Phone, LiveChat, Email), CRM Systems (Dynamics365)} \\
     \textbf{Communication}       {: Content Creation, Social Media Operations, Video Production, Brand Advocacy, Digital Communication, Editing} \\
     \textbf{Technical \& Office} {: Microsoft Office (Word, Excel, PowerPoint), Figma, Notion, Trello, Adobe Creative Suite, Canva} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}