%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.5cm,right=1.5cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Roel-Junior Alejo Viernes}
\tagline{Computer Science BSc (Hons) Graduate}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \homepage{www.rjviernes.tech}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  \location{London, United Kingdom}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
   \github{github.com/rjviernes620} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
 \linkedin{linkedin.com/in/rjviernes620}
}
%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection{Personal Statement}
Computer Science graduate (2:1) and multidisciplinary Creative Technologist specializing in the intersection of 
Machine Learning, Human-Computer Interaction and digital storytelling. 
From developing real-time Computer Vision systems (HandTyper) to leading technical video production
for the University of Greenwich, I excel at translating complex engineering principles into
high-fidelity user experiences. Seeking to leverage my background in Python, ML,
and professional media production to build the next generation of AI-driven creative tools.
\\



\cvsection{Projects}
\smallskip

\textbf{Final Year Project: HandTyper - Hand Gesture based PC Interaction} \\
\begin{itemize}
  \item Engineered a real-time gesture recognition system using Python, Mediapipe, and TensorFlow, enabling full PC control (mouse and keyboard) via high-fidelity hand tracking.
  \item Developed a custom BSL (British Sign Language) translation layer, utilizing landmark detection to interpret complex hand signals into real-time digital inputs.
  \item Implemented landmark detection to track hand points, facilitating accurate estimation of user gestures for seamless translation into mouse and keyboard actions.
  \item Optimized model performance for low-latency video feeds, ensuring smooth human-computer interaction across standard webcam hardware.
\end{itemize}

\smallskip
\textbf{University Open Day Guides w/ NFC Tags} \\
\begin{itemize}
  \item To assist prospective students during the University Open Days whilst upholding the university's
   commitment to sustainability. I introduced a new interaction framework where staff members would 
   have NFC tags linking towards a digital guide for the University and the relevant event. 
  \item This reduced the need for approx. 300+ printed materials per event and allowed for easy access to information via 
   smartphones.
\end{itemize}
\textbf{Coursework Project: TAS Speedruns and the use of AI in Games} \\
\begin{itemize}
  \item Developed an autonomous AI agent for Super Mario Bros using the Monte Carlo Tree Search (MCTS) algorithm to optimize pathfinding and level completion speed.
  \item Researched and implemented various Machine Learning algorithms to control CPU behavior, focusing on rapid decision-making in dynamic video game environments.
  \item Achieved high-efficiency pathfinding by training agents to navigate complex obstacles and enemy patterns in the fastest time possible.
\end{itemize}

\cvsection{Experience}

\cvevent{Faculty Social Media Assistant}{University of Greenwich}{June 2023 - Oct 2025}{Greenwich, London}
\begin{itemize}
\item Multidisciplinary Production: Managed the full lifecycle of technical video content for the Faculty of Engineering \& Science, bridging the gap between deep-tech research and user-facing digital storytelling.
\item Stakeholder Management: Partnered with Professors and Researchers to storyboard and render accessible content for major university campaigns.
\item Brand Growth: Owned social media channel management for the faculty, increasing publication frequency through streamlined content workflows.
\item \textbf{Key Achievement: 2024/25 Clearing Campaigns:}
\item Spearheaded the short-form video strategy, producing testimonials and facility showcases that drove audience engagement across faculty platforms.
\item Collaborated with central marketing to ensure 100\% brand consistency while translating complex engineering concepts for prospective students.
\end{itemize}

\divider

\cvevent{Senior UK Student Recruitment Ambassador}{University of Greenwich}{May 2023 -- Oct 2025}{Greenwich, London}
\begin{itemize}
\item Team Leading: Led a team of 10+ staff/student ambassadors in clearing operations and day-to-day customer service, ensuring a high-quality 
experience for prospective students and their families during high-pressure periods.
\item External Engagement: Represented the university at external events, including UCAS fairs, Panels, and school visits, effectively communicating the value of the university's offerings to a wide range of audiences.
\item Operational Excellence: Assisted in the planning of certain outreach initiatives, contributing to the university's recruitment goals through efficient planning and execution.

\end{itemize}

%\cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}

\cvsection{Education}

\cvevent{BSc (Hons) - Computer Science - 2:1}{University Of Greenwich}{Sep 22 -- Jul 25}{Greenwich, London}
\begin{itemize}
    \item Modules inc. HCI, Machine Learning, AI, Software Engineering, Data Structures, Advanced Programming, Operating Systems
\end{itemize}

\cvevent{A Level}{University of Kent Academies Trust}{Sep 20 -- Jun 22}{Gillingham, Kent}
\begin{itemize}
    \item Information Technology (D*), Business Studies (D*), Finance (BB) | 152 UCAS points
\end{itemize}

\cvsection{Volunteering}
\cvevent{Society President}{comptech.gre (Greenwich Students Union)}{Sep 24 - Jul 25}{Greenwich, London}

\cvevent{Programme Representative}{Greenwich Students Union}{Sep 23 - Jul 24}{Greenwich, London}

\cvsection{Interests}
\cvproject{Technical}
\begin{itemize}
\item Human Computer Interaction, Cloud Computing, Machine Learning, Video Editing
\end{itemize}

\cvproject{Hobbies}
\begin{itemize}
\item Content Creation, Music, Traveling, Gaming
\end{itemize}

\cvsection{Skills}
\cvskill{English}{5}
\cvskill{Tagalog/Filipino}{4}
\cvskill{Spanish}{2}

\end{document}
